Analysis of Ontario Wildlife Harvests and Active Hunters

### 2024-04-04 paper/paper.qmd
Updated quarto heading and cleaned moose data

---
title: "Analysis of Ontario Wildlife Hunting Data"
subtitle: "2009-2023"
author: Samantha Barfoot
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction

>>>>

---
title: "Analysis of Ontario Wildlife Harvests and Active Hunters"
subtitle: "2009-2023"
author: Samantha Barfoot
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction
